\documentclass[a4paper,10pt]{article}
%\usepackage[margin=0.5in]{geometry}
\usepackage{fullpage}
\usepackage{array}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{gensymb}
\newcolumntype{K}{>{\centering\arraybackslash}r}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{0.5em}{}[{\titlerule[0.4pt]}]

\begin{document}
	
	\begin{center}
		{\Large\bfseries Abra\~ao Pacheco Dos Santos Peres Mota} \\
		\vspace{2mm}
		{\textbf{Tel:} +44 79 444 651 32  } {\textbf{E-mail:} abraaomot@outlook.com } \\ \vspace{1mm}
	Senior full stack engineer \&  system architect with a passion for technical excellence
	\end{center}

	\section*{Education}

\begin{tabular}{rl}	
	2014-2018 & \textbf{Imperial College London}, London, United Kingdom \\& 
	\textbf{Computing MEng - First Class Honours} \\&\\& 
	\textbf{Horizons Language Courses}: Russian Level 1 - Merit, Spanish Level 4 - Merit
	\\\multicolumn{2}{c}{} \\
	2012-2014 & \textbf{Chelsea Academy}, London, United Kingdom \\&
	\textbf{A-Levels:}
	Maths, Further Maths, Physics, Economics (AS only) -A*AAB 
	\\\multicolumn{2}{c}{} \\
	2007-2012 & \textbf{Battersea Park School}, London, United Kingdom \\& 
	\textbf{GCSEs:} 11 A*'s, Latin, Spanish- AA*, \textbf{AS:} Portuguese - A
	\\\multicolumn{2}{c}{} \\
	
\end{tabular}

	
	\section*{Work Experience}
	
		\textbf{Goldman Sachs - Asset Management Client Services Engineering}
		\\\textbf{Executive Director}  \hfill Jan 2023 - Current 
		\\ - Have led a team 8 devs since January. Developed \& executed on a strategic roadmap to fulfill reporting obligations, as well as design the team-wide data strategy. We are building out a new pipeline, leveraging a Datalake \& handling 40+ load-balanced API's to serve data to various internal customers thousands of times a day. This strategy additionally aligns to the demise of several legacy systems by consolidating data sourcing into a single ownership model.
		\\ - Have used a variety of technologies in my tenure, including \textbf{Java, Python, Kubernetes, MongoDB, SybaseIQ, MemSQL, Kafka, SpringBoot, Angular, SQL, Graph Databases} to name a few.
		\\\\
		\textbf{Associate}  \hfill Jan 2020 - Dec 2022
		\\ - Led a 6 month integration with a vendor to overhaul the client servicing strategy for a product line. I co-ordinated a team of contractors to deliver on stakeholder requirements, while unblocking the project from technical \& compliance risks. Also implemented \textbf{migration strategy of 30k+ historical records} into the new system, which has handled \textbf{100k+ enquiries since go-live}. The system now captures customer analytics and has digitised phone enquiries via AWS Connect.
		\\ - Upgraded the infrastructure of our flagship microservice application to a containerised solution using \textbf{Kubernetes}. This created SSL certificates for all environments \& load-balances business critical traffic with \textbf{3 9's uptime}. This implementation paved the way for containerisation of 3+ apps since.
		\\ - Designed \& implemented a SpringBoot service that tagged \& stored client uploaded documents with high uptime \& availability requirements. The service has reliably scaled with the increase of external, client-facing traffic. This used Kafka, Amazon S3, MemSQL \& MongoDB.
		\\ - Have sought to coach others by leading intern projects \& encouraged technical excellence within my team by instituting monthly calls to discuss software craft,  new technologies \& other topics of interest.
		\\\\
		\textbf{Analyst}  \hfill Jul 2018 - Dec 2019
		\\ - Digitised 2 large-scale client onboarding workflows, resulting in operational \textbf{multi-HC savings}. 
		\\ - I have also implemented an OCR solution to hydrate workflows based on client submitted data, resulting in \textbf{100's of hours operational savings per year} as well as reducing double-keying risk.
		\\\\\hfill\textbf{Unboxed / char.gy} 
		\\\textbf{Software Developer} \hfill Apr 2017 - Sep 2017 
		\\ - Worked on a variety of Ruby on Rails projects, including security patches \& frontend updates to the UK Government Petitions website. 
		\\ - Created a simple CMS leveraging AWS S3 which hosted images for the internal company blog. 
		\\ - I contributed to the alpha \& beta stages of char.gy, an EV charging startup. This included enhancements in communication protocols to the charging point \& marketing email tracking enhancements to improve user nurturing journeys, as well as direct customer face-off.
		\\\\	
		\textbf{Alliants}
		\\\textbf{Software Developer Intern} \hfill Jul 2016 - Sep 2016
		\\ - I created a tool using Ruby on Rails to store organisational information.
		\\\\
		\textbf{Self Employed} 
		\\\textbf{Private Tutor} \hfill Oct 2014 - Jun 2016 
		\\ I have taught 2 pupils at GCSE level for a year each, a minimum weekly 4 hour commitment.

		
		

	

	
		\section*{Skills}
	
	\begin{tabular}{r|p{12cm}}	
		\textbf{Computing}	 & \textbf{Programming} - Java, Python, Ruby, SpringBoot  \\&
								\textbf{Web Development} - Angular, Ruby on Rails, Bootstrap, HTML \& CSS \\&
								\textbf{Infra \& other} - Kubernetes, Kafka, Database design, REST API's, MongoDB, MemSQL, SybaseIQ  \\
		\textbf{Languages}   & \textbf{Portuguese} - Native, \textbf{English} - Native, \textbf{Spanish} - Advanced
	\end{tabular}
	
	\section*{Projects}
	
	\begin{tabular}{r|p{12cm}}
		
		May-June 2016  & \textbf{Summit} \\& Summit is a web application platform designed using Agile methods to help people learn how to trade using real time data from real stocks. This was a 4 person project, developed in partnership with Flextrade. I largely worked on the frontend which made extensive use of Javascript, React.js and Bootstrap.
		\\\multicolumn{2}{c}{} \\
		
		January 2016 & \textbf{MyoGaming at ICHACK 2016 Hackathon} \\&
		This 24-hour hackathon culminated in an android game where the user could wear a VR headset and shoot at enemies using the Myo armband. We used bluetooth \& custom API's to control the game on the user's phone.
	\end{tabular}

	
	
	
\end{document}
