\documentclass[a4paper,10pt]{article}
%\usepackage[margin=0.5in]{geometry}
\usepackage{fullpage}
\usepackage{array}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{gensymb}
\newcolumntype{K}{>{\centering\arraybackslash}r}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{0.5em}{}[{\titlerule[0.4pt]}]

\begin{document}
	
	\begin{center}
		{\large\bfseries Abra\~ao Mota} \\

		{\textbf{Tel:} +44 79 444 651 32  } {\textbf{E-mail:} abraaomot@outlook.com } \\ 
	Full stack engineer \&  system architect with a passion for technical excellence
	\end{center}

	\section*{Education}_
		
		\textbf{Imperial College London}, London, United Kingdom \hfill \textit{2014 - 2018}
		
		\textbf{Computing MEng - First Class Honours} 
	

		\textbf{A-Levels:} Maths, Further Maths, Physics, Economics (AS only) -A*AAB  \hfill \textit{2012 - 2014 }
		
		
		
	
	
	
	
	\section*{Work Experience}
	
	\textbf{\textit{\underline{Goldman Sachs - Asset Management - Client Services Engineering}}}
		\\\textbf{Lead Software Engineer - (Executive Director)}  \hfill \textit{Jan 2023 - Current }
		\\ - Have led a team of 8 devs since January. Executed on a strategic roadmap to fulfill regulatory \& client reporting obligations. More recently, have re-designed the team data strategy, leveraging new ETL/ELT techniques, using a Datalake \& handling 40+ load-balanced API's to serve data to various internal customers. This also aligns to the decommission of legacy systems by consolidating data sourcing.
		\\ - Have used a variety of technologies in my tenure, including \textbf{Java, Python, Kubernetes, MongoDB, SybaseIQ, MemSQL, Kafka, SpringBoot, Angular, SQL, Graph Databases} to name a few.
		\\\\
		\textbf{Software Engineer - (Associate)}  \hfill \textit{Jan 2020 - Dec 2022}
		\\ - Led a 6 month integration with a vendor to overhaul the global client servicing strategy for a product line. I co-ordinated a team of 6, unblocking the project from technical \& compliance risks. Used \textbf{Python} to tactically \textbf{migrate 30k+ historical customer service records} into the new system, which has handled \textbf{100k+ enquiries since go-live}. The new system now captures customer analytics and has digitised phone enquiries via AWS Connect.
		\\ - Upgraded the infrastructure of our flagship microservice application to a containerised solution using \textbf{Kubernetes}. This created SSL certificates for all environments \& load-balances business critical traffic with \textbf{3 9's uptime}. This implementation paved the way for containerisation of 3+ apps since.
		\\ - Designed \& implemented a SpringBoot service that tagged \& stored client uploaded documents with high uptime \& availability requirements. The service has reliably scaled with the increase of external, client-facing traffic. This used \textbf{Kafka, Amazon S3, MemSQL \& MongoDB}.
		\\ - Have sought to coach others by leading intern projects \& encouraged technical excellence within my team by instituting monthly calls to discuss software craft,  new technologies \& other topics of interest.
		\\\\
		\textbf{Software Engineer - (Analyst)}  \hfill \textit{Jul 2018 - Dec 2019}
		\\ - Digitised 2 large-scale client onboarding workflows, resulting in operational \textbf{multi-HC savings}. 
		\\ - I have also implemented an OCR solution to hydrate workflows based on client submitted data, resulting in \textbf{100's of hours operational savings per year} and reduced double-keying risk.
		\\\\\hfill\textbf{\textit{\underline{Unboxed / char.gy}}}
		\\\textbf{Software Developer - (Internship)} \hfill \textit{Apr 2017 - Sep 2017 }
		\\ - Worked on UK Gov. petitions website - security patches \& frontend updates. Developed for Char.gy, an EV startup - charging point protocol enhancements, marketing email tracking \& customer face-off.
	
		

	

	
		\section*{Skills}
	
	\begin{tabular}{r|p{12cm}}	
		\textbf{Computing}	 & \textbf{Programming} - Java, SpringBoot (Fluent), Python (Proficient), Ruby, Javascript, C, Haskell (Past Experience) \\&
								\textbf{Infra \& other} - Kubernetes, Kafka, Database design, REST API's, MongoDB, MemSQL, SybaseIQ, AWS S3, Angular, Ruby on Rails  \\
		\textbf{Languages}   & \textbf{Portuguese} - Native, \textbf{English} - Native, \textbf{Spanish} - Advanced
	\end{tabular}
	
	\thispagestyle{empty}

	
	
\end{document}
